The promise of community-driven preprints in ecology and evolution

### 2024-10-22 ms/ms.qmd
Few final fixes before render

```{r, fig-summary}
#| label: fig-summary
#| fig-cap: "Summary of articles posted to *EcoEvoRxiv*. A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023. *EcoEvoRxiv* was established in June 2018 before the launch in November 2018. Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of articles uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa covered in the articles posted to *EcoEvoRxiv* (*n* = 1080 articles covering relevant taxa); D) Types of articles accepted on *EcoEvoRxiv* (*n* = 1216 articles). E) Academic age of authors posting preprints to *EcoEvoRxiv* (*n* = 1135 published and unpublished preprints) along with the gender of the submitting author. Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal. Map base source: R Package maps v.3.4.2. Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/."

@@

# How many preprints remain unpublished? (preprints only)
unpub <- nrow(preprints) - nrow(preprints_pub_only)
per_unpublished <- nrow(preprints_pub_only)/ nrow(preprints)

>>>>

```{r, fig-summary}
#| label: fig-summary
#| fig-cap: "Summary of articles posted to *EcoEvoRxiv*. A) Number of articles (preprints and postprints) published on *EcoEvoRxiv* between 2018 and 2023. *EcoEvoRxiv* was established in June 2018 before the launch in November 2018. Notable milestones include *EcoEvoRxiv* transitioning to the California Digital Library (CDL), the acceptance of preprints and postprints in Spanish and Portuguese, and the acceptance of the first IUCN Red List Ecosystem report; B) Geographic origin of articles uploaded to *EcoEvoRxiv*, inferred from the country of affiliation of the submitting author; C) Taxa covered in the articles posted to *EcoEvoRxiv* (*n* = 1080 articles covering relevant taxa); D) Types of articles accepted on *EcoEvoRxiv* (*n* = 1216 articles). E) Academic age of authors posting preprints to *EcoEvoRxiv* (*n* = 1135 published and unpublished preprints) along with the gender of the submitting author. Values lower than zero are indicative of authors who uploaded preprints before their first scientific publication in a journal. Map base source: R Package maps v.3.4.2. Shapefile: Natural Earth https://www.naturalearthdata.com/about/terms-of-use/."
#| echo: false
#| warning: false
#| message: false

@@

# How many preprints remain unpublished? (preprints only)
          unpub <- nrow(preprints) - nrow(preprints_pub_only)
per_unpublished <- unpub / nrow(preprints)
